---
title: ""
toc: false
editor: source
freeze: false
---

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(gsheet)
library(tidyverse)

MEDIA_SHEET_URL <- "https://docs.google.com/spreadsheets/d/1id1P5ke9ZJckr_6ePP84FOLeQPoHb57eitX7yaZ_l8A/edit#gid=625135132"
PUBS_SHEET_URL  <- "https://docs.google.com/spreadsheets/d/1id1P5ke9ZJckr_6ePP84FOLeQPoHb57eitX7yaZ_l8A/edit#gid=1000751275"

html_esc <- function(x) {
  x <- gsub("&", "&amp;", as.character(x))
  x <- gsub("<", "&lt;", x)
  x <- gsub(">", "&gt;", x)
  x
}

media   <- gsheet2tbl(MEDIA_SHEET_URL) %>% arrange(desc(year))
profile <- Sys.getenv("QUARTO_PROFILE", unset = "en")
```

::: {.content-visible when-profile="en"}
This page collects media appearances — interviews, press coverage, and radio segments — as well as outreach articles written for general audiences. Most interviews and press coverage are in Spanish, from Argentine media.

### Interviews & press
:::
::: {.content-visible when-profile="es"}
Esta página reúne apariciones en medios —entrevistas, notas de prensa y segmentos de radio— y artículos de divulgación escritos para el público general.

### Entrevistas y prensa
:::

```{r interviews, results='asis'}
#| echo: false

media_cards <- media %>% filter(year >= 2025)
media_list  <- media %>% filter(year < 2025)

# ---- Featured cards: 2025+ ----
if (nrow(media_cards) > 0) {
  cat('<div class="media-cards-grid">\n')
  for (i in seq_len(nrow(media_cards))) {
    m <- media_cards[i, ]
    title_html <- html_esc(as.character(m$title))

    has_img <- "img" %in% names(m) && !is.na(m$img) && trimws(as.character(m$img)) != ""
    img_html <- if (has_img)
      paste0('<img class="media-card-img" src="', trimws(as.character(m$img)), '" alt="">\n')
    else
      '<div class="media-card-img-placeholder"></div>\n'

    title_linked <- if (!is.na(m$url) && trimws(as.character(m$url)) != "")
      paste0('<a href="', m$url, '">', title_html, '</a>')
    else title_html

    medio_str <- if (!is.na(m$medio) && trimws(as.character(m$medio)) != "")
      paste0('<span class="media-card-medio">', html_esc(as.character(m$medio)), '</span> · ')
    else ""

    # url2 as secondary link pill (title already links to url)
    links <- character(0)
    if (!is.na(m$url2) && trimws(as.character(m$url2)) != "")
      links <- c(links, paste0('<a href="', m$url2, '">link 2</a>'))
    links_html <- if (length(links) > 0)
      paste0('<span class="pub-links">', paste(links, collapse = ""), '</span>\n') else ""

    cat(paste0(
      '<div class="media-card">\n',
      img_html,
      '<div class="media-card-body">\n',
      '<div class="media-card-title">', title_linked, '</div>\n',
      '<div class="media-card-meta">', medio_str, as.character(m$year), '</div>\n',
      links_html,
      '</div>\n',
      '</div>\n\n'
    ))
  }
  cat('</div>\n\n')
}

# ---- Archive list: pre-2025 ----
if (nrow(media_list) > 0) {
  if (nrow(media_cards) > 0) {
    label <- if (profile == "es") "Anteriores" else "Earlier"
    cat(paste0('<p class="media-archive-label">', label, '</p>\n'))
  }

  cat('<div class="research-list">\n')
  prev_year <- ""
  for (i in seq_len(nrow(media_list))) {
    m <- media_list[i, ]
    yr <- as.character(m$year)
    year_label <- if (yr != prev_year) yr else ""
    cont_class <- if (year_label == "") " pub-cont" else ""
    prev_year  <- yr

    title_html <- html_esc(as.character(m$title))

    medio_html <- if (!is.na(m$medio) && m$medio != "")
      paste0('<div class="pub-author-row"><em>', html_esc(as.character(m$medio)), '</em></div>\n')
    else ""

    links <- character(0)
    if (!is.na(m$url)  && m$url  != "") links <- c(links, paste0('<a href="', m$url,  '">link</a>'))
    if (!is.na(m$url2) && m$url2 != "") links <- c(links, paste0('<a href="', m$url2, '">link 2</a>'))
    links_html <- if (length(links) > 0)
      paste0('<span class="pub-links">', paste(links, collapse = ""), '</span>\n') else ""

    cat(paste0(
      '<div class="pub-entry', cont_class, '">\n',
      '<span class="pub-year-col">', year_label, '</span>\n',
      '<div class="pub-body">\n',
      '<div class="pub-title-row">', title_html, '</div>\n',
      medio_html,
      links_html,
      '</div>\n',
      '</div>\n\n'
    ))
  }
  cat('</div>\n\n')
}
```

::: {.content-visible when-profile="en"}
### Articles & outreach
:::
::: {.content-visible when-profile="es"}
### Artículos de divulgación
:::

```{r outreach, results='asis'}
#| echo: false

outreach <- gsheet2tbl(PUBS_SHEET_URL) %>%
  filter(type == "media") %>%
  arrange(desc(year))

cat('<div class="research-list">\n')
prev_year <- ""
for (i in seq_len(nrow(outreach))) {
  p <- outreach[i, ]
  yr <- as.character(p$year)
  year_label <- if (yr != prev_year) yr else ""
  cont_class <- if (year_label == "") " pub-cont" else ""
  prev_year  <- yr

  title_html <- if (!is.na(p$url) && p$url != "")
    paste0('<a href="', p$url, '">', html_esc(as.character(p$title)), '</a>')
  else html_esc(as.character(p$title))

  journal_html <- if (!is.na(p$journaltitle) && p$journaltitle != "")
    paste0('<div class="pub-journal-row">', html_esc(as.character(p$journaltitle)), '</div>\n')
  else ""

  cat(paste0(
    '<div class="pub-entry', cont_class, '">\n',
    '<span class="pub-year-col">', year_label, '</span>\n',
    '<div class="pub-body">\n',
    '<div class="pub-title-row">', title_html, '</div>\n',
    journal_html,
    '</div>\n',
    '</div>\n\n'
  ))
}
cat('</div>\n\n')
```
