---
title: ""
toc: false
editor: source
freeze: false
---

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(gsheet)
library(tidyverse)

SHEET_URL <- "https://docs.google.com/spreadsheets/d/1id1P5ke9ZJckr_6ePP84FOLeQPoHb57eitX7yaZ_l8A/edit#gid=852428719"
```

::: {.content-visible when-profile="en"}
I have taught undergraduate and graduate courses at the University of Buenos Aires and Torcuato Di Tella University, covering statistics, Bayesian inference, data visualization, and behavioral science. I have also led training workshops on statistical literacy for public officials and journalists. My teaching aims to connect rigorous quantitative methods with real-world reasoning and decision-making.

### Interactive Apps

A collection of experiments and visualizations built for the course *Neurociencia y Psicología Experimental* at Torcuato Di Tella University. Try them in your browser — no installation needed.

<div class="apps-grid">
  <a href="https://gsolovey-utdt.github.io/two-armed-bandit/" class="app-card">
    <div class="app-name">Two-Armed Bandit</div>
    <div class="app-type">experiment</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/stroop/" class="app-card">
    <div class="app-name">Stroop</div>
    <div class="app-type">experiment</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/azar/" class="app-card">
    <div class="app-name">Gambling Game</div>
    <div class="app-type">experiment</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/umbral-de-deteccion/" class="app-card">
    <div class="app-name">Detection Threshold</div>
    <div class="app-type">experiment</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/memoria-de-digitos/" class="app-card">
    <div class="app-name">Digit Memory</div>
    <div class="app-type">experiment</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/correlacion/" class="app-card">
    <div class="app-name">Correlation</div>
    <div class="app-type">visualization</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/asignacion_aleatoria/" class="app-card">
    <div class="app-name">Random Assignment</div>
    <div class="app-type">visualization</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/muestreo_aleatorio/" class="app-card">
    <div class="app-name">Random Sampling</div>
    <div class="app-type">visualization</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/set/" class="app-card">
    <div class="app-name">Set</div>
    <div class="app-type">game</div>
  </a>
</div>

### Courses
:::

::: {.content-visible when-profile="es"}
Dicté cursos de grado y posgrado en la Universidad de Buenos Aires y la Universidad Torcuato Di Tella, en áreas como estadística, inferencia bayesiana, visualización de datos y ciencias del comportamiento. También coordiné capacitaciones sobre alfabetización estadística para funcionarios públicos y periodistas. Mi enfoque busca conectar métodos cuantitativos rigurosos con el razonamiento y la toma de decisiones en contextos reales.

### Aplicaciones interactivas

Una colección de experimentos y visualizaciones desarrollados para el curso *Neurociencia y Psicología Experimental* en la Universidad Torcuato Di Tella. Se pueden usar directamente en el navegador, sin instalación.

<div class="apps-grid">
  <a href="https://gsolovey-utdt.github.io/two-armed-bandit/" class="app-card">
    <div class="app-name">Two-Armed Bandit</div>
    <div class="app-type">experimento</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/stroop/" class="app-card">
    <div class="app-name">Stroop</div>
    <div class="app-type">experimento</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/azar/" class="app-card">
    <div class="app-name">Juego del Azar</div>
    <div class="app-type">experimento</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/umbral-de-deteccion/" class="app-card">
    <div class="app-name">Umbral de Detección</div>
    <div class="app-type">experimento</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/memoria-de-digitos/" class="app-card">
    <div class="app-name">Memoria de Dígitos</div>
    <div class="app-type">experimento</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/correlacion/" class="app-card">
    <div class="app-name">Correlación</div>
    <div class="app-type">visualización</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/asignacion_aleatoria/" class="app-card">
    <div class="app-name">Asignación Aleatoria</div>
    <div class="app-type">visualización</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/muestreo_aleatorio/" class="app-card">
    <div class="app-name">Muestreo Aleatorio</div>
    <div class="app-type">visualización</div>
  </a>
  <a href="https://gsolovey-utdt.github.io/set/" class="app-card">
    <div class="app-name">Set</div>
    <div class="app-type">juego</div>
  </a>
</div>

### Cursos
:::

```{r teaching, results='asis'}
#| echo: false

courses <- gsheet2tbl(SHEET_URL) %>%
  filter(cargo %in% c("prof", "doc")) %>%
  arrange(desc(year))

html_esc <- function(x) {
  x <- gsub("&", "&amp;", as.character(x))
  x <- gsub("<", "&lt;", x)
  x <- gsub(">", "&gt;", x)
  x
}

cat('<div class="research-list">\n')
prev_year <- ""
for (i in seq_len(nrow(courses))) {
  c_row <- courses[i, ]
  yr    <- as.character(c_row$year)
  year_label <- if (yr != prev_year) yr else ""
  cont_class <- if (year_label == "") " pub-cont" else ""
  prev_year  <- yr

  materia_html <- if (!is.na(c_row$url) && c_row$url != "")
    paste0('<a href="', c_row$url, '">', html_esc(c_row$materia), '</a>')
  else html_esc(as.character(c_row$materia))

  cat(paste0(
    '<div class="pub-entry', cont_class, '">\n',
    '<span class="pub-year-col">', year_label, '</span>\n',
    '<div class="pub-body">\n',
    '<div class="pub-title-row">', materia_html, '</div>\n',
    '<div class="pub-author-row">', html_esc(as.character(c_row$carrera)), '</div>\n',
    '</div>\n',
    '</div>\n\n'
  ))
}
cat('</div>\n\n')
```
